Testing Set Features Visualization

### 2022-10-16 TestingPipeline/Scripts/testing_set_features_visualization.Rmd
Contribution of individual tuning rules.

>>>>

use of each tuning rule
```{r}
keep_score <- rep(0, nrow(viruses))

keep_score[viruses$hallmark>2] <- keep_score[viruses$hallmark>2] + 1
table(keep_score, viruses$seqtype)
keep_score[viruses$checkv_host_genes>50 & viruses$checkv_provirus=="No"] <- keep_score[viruses$checkv_host_genes>50 & viruses$checkv_provirus=="No"] - 1
table(keep_score, viruses$seqtype)
keep_score[viruses$percent_unknown>=75 & viruses$checkv_length<50000] <- keep_score[viruses$percent_unknown>=75 & viruses$checkv_length<50000] + 0.5
table(keep_score, viruses$seqtype)
keep_score[viruses$percent_viral>=50] <- keep_score[viruses$percent_viral>=50] + 0.5
table(keep_score, viruses$seqtype)
    #keep_score[viruses$hallmark>=(viruses$checkv_viral_genes/5)] <- keep_score[viruses$hallmark>=(viruses$checkv_viral_genes/5)] + 1 #add some ratio
keep_score[viruses$checkv_viral_genes==0 & viruses$checkv_host_genes>=1] <- keep_score[viruses$checkv_viral_genes==0 & viruses$checkv_host_genes>=1] - 1
table(keep_score, viruses$seqtype)
keep_score[((viruses$checkv_viral_genes*3) <= viruses$checkv_host_genes) & viruses$checkv_provirus=="No"] <- keep_score[((viruses$checkv_viral_genes*3) <= viruses$checkv_host_genes) & viruses$checkv_provirus=="No"] - 1 # consider accounting for provirus designation
table(keep_score, viruses$seqtype)
#    keep_score[(viruses$checkv_viral_genes*3) <= viruses$checkv_host_genes] <- 0 # consider accounting for provirus designation
keep_score[viruses$checkv_length>500000 & viruses$hallmark==0] <- keep_score[viruses$checkv_length>500000 & viruses$hallmark==0] - 1
table(keep_score, viruses$seqtype)
```
